---
title: "BIA results - changing costs"
output:
  pdf_document: default
  html_document: default
---

### Load required functions ###

```{r, echo=FALSE, message=FALSE, warning=FALSE}

  library(epicR)
  library(tidyverse)
  library(dplyr)
  library(ggplot2)
  library(gridExtra)
  library(ggpubr)
  library(knitr)
  library(kableExtra)

```


### Global settings and input values ###

Note: time_horizon is the simulation time horizon not the analysis time horizon.
The analysis time horizon is 5 years (2022-2026) but since EPIC starts in 2015 the 
modelling time horizon is 13 (only need 12 but run one more year than needed 
because the final year results get messed up).
The time horizon of the budget impact analysis can be entered by using the
CD_start_cal_year and CD_end_cal_year parameters. 


```{r global settings, echo=FALSE}


  record_mode <- c(record_mode_none=0,
                   record_mode_agent=1,
                   record_mode_event=2,
                   record_mode_some_event=3)

  settings <- get_default_settings()
  
  settings$record_mode <- record_mode["record_mode_none"] # stores the events matrix, switch to "record_mode_none" for faster code
  settings$n_base_agents <- 10000 # 2015 estimate tuned to produce 2022 cohort size matching Stats Canada population estimates https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1710000501
  settings$n_base_agents <- settings$n_base_agents - 1 # -1 since it starts at id=0 
  settings$update_continuous_outcomes_mode <- 1

  

  # * common input values ---------------------------------------------------
  # these input values all remain constant across case detection scenarios
  time_horizon <- 13
  yrs_btw_CD <- 20 # ensures no individual tested twice; change this if want to consider repeat testing
  CD_start_cal_year <- 2022 # calendar start year
  CD_start_year <- CD_start_cal_year - 2015 # simulation start year; default is 50 i.e. no case detection
  CD_end_cal_year <- 2026
  CD_end_year <- CD_end_cal_year - 2015 # default is 50 i.e. no case detection
  discount_rate <- 0 # the default
  med_adherence <- 0.7 # the default, adjust for sensitivity analysis
  smoking_adherence <- 0.7 # adherence to NRT; the default, adjust for sensitivity analysis
  p_case_detection <- c(0.05,0.1,0.15,0.2,0.25) # uptake parameter
  p_correct_overdiagnosis <- 0.67 # did my own validation on this
  price_yr <- 1.030665381 # 2021 average ; was OG 1.03761 = Jan 2022 (so not very different but I think 2021 makes more sense)
  
  
  
  # set buffer sizes - below needed for identical pre-intervention simulation runs
  settings$random_number_agent_refill <- 1
  settings$runif_buffer_size <- time_horizon*70 
  settings$rexp_buffer_size <- time_horizon*140 
  settings$rnorm_buffer_size <- time_horizon*8 + 10 
  settings$rgamma_buffer_size <- time_horizon + 2 

```




### Simulation function ###

Function for simulating the case detection scenarios.

Function inputs:
  - CD_method : "None" "CDQ17" "CDQ195" "CDQ165" "FlowMeter" "FlowMeter_CDQ"
  - eligibility_criteria : "All patients" "Symptomatic" "Eversmokers"

Function output:
  - overall : cumulative results across the entire time horizon (number agents, number diagnosed, and number eligible for case detection);
              these are needed for table 3 of the main article
  - results - annual results


```{r functions, echo=FALSE}

# * EPIC simulation ------------------------------------------------------------



  BIA_simul <- function(CD_method, eligibility_criteria){
    
    CD_method="CDQ17" ; eligibility_criteria="All patients"

    if(!CD_method %in% c("None", "CDQ17", "CDQ195", "CDQ165", "FlowMeter", "FlowMeter_CDQ")){
      print("Unknown case detection method")
    }

    ### run simulation
    init_session(settings=settings)
    input <- get_input()

    if(eligibility_criteria=="All patients"){
      min_age <- 40
      min_pack_years <- 0
      num_symptoms <- 0
      CD_values <- input$values$diagnosis$case_detection_methods[,CD_method]
    }else if (eligibility_criteria=="Symptomatic"){
      min_age <- 40
      min_pack_years <- 0
      num_symptoms <- 1
      CD_values <- input$values$diagnosis$case_detection_methods_symptomatic[,CD_method]
    }else if (eligibility_criteria=="Eversmokers"){
      min_age <- 50
      min_pack_years <- 0.001
      num_symptoms <- 0
      CD_values <- input$values$diagnosis$case_detection_methods_eversmokers[,CD_method]
    }else{
      terminate_session()
      return("Unknown eligibility criteria")
    }

    input$values$global_parameters$time_horizon <- time_horizon 
    input$values$diagnosis$case_detection_start_end_yrs <- c(CD_start_year, CD_end_year)
    input$values$diagnosis$years_btw_case_detection <- yrs_btw_CD
    input$values$global_parameters$discount_cost <- discount_rate
    input$values$medication$medication_adherence <- med_adherence
    input$values$smoking$smoking_cessation_adherence <- smoking_adherence
    if(CD_method!="None"){
    input$values$diagnosis$p_case_detection[(CD_start_year+1):(CD_start_year+length(p_case_detection))] <- p_case_detection
    }
    input$values$diagnosis$p_correct_overdiagnosis <- p_correct_overdiagnosis

    input$values$diagnosis$min_cd_age <- min_age
    input$values$diagnosis$min_cd_pack_years <- min_pack_years
    input$values$diagnosis$min_cd_symptoms <- num_symptoms

    input$values$cost$cost_case_detection <- CD_values[3]*price_yr
    input$values$diagnosis$logit_p_prevalent_diagnosis_by_sex["case_detection.None",] <- CD_values[1]
    input$values$diagnosis$logit_p_diagnosis_by_sex["case_detection.None",] <- CD_values[1]
    input$values$diagnosis$logit_p_overdiagnosis_by_sex["case_detection.None",] <- CD_values[2]

    input$values$cost$bg_cost_by_stage <- input$values$cost$bg_cost_by_stage*price_yr
    input$values$cost$cost_smoking_cessation <- input$values$cost$cost_smoking_cessation*price_yr
    input$values$cost$exac_dcost <- input$values$cost$exac_dcost*price_yr
    input$values$cost$cost_outpatient_diagnosis <- input$values$cost$cost_outpatient_diagnosis*price_yr
    input$values$cost$cost_gp_visit <- input$values$cost$cost_gp_visit*price_yr
    input$values$medication$medication_costs <- input$values$medication$medication_costs*price_yr

    set.seed(333)
    run(input = input$values)

    output <- Cget_output()
    output_ex <- Cget_output_ex()

    terminate_session()


    # number alive
    base <- data.frame(year=1:(time_horizon),
                       criteria=eligibility_criteria,
                       CD_method=CD_method,
                       alive=rowSums(output_ex$n_alive_by_ctime_sex),
                       sex=output_ex$n_alive_by_ctime_sex[,2],
                       smoke=output_ex$n_smoking_status_by_ctime[,2]
    )

    # number with COPD and diagnosed
    diags <- data.frame(copd=rowSums(output_ex$n_COPD_by_ctime_severity[,2:5]),
                        copd_GOLD1=output_ex$n_COPD_by_ctime_severity[,2],
                        copd_GOLD2=output_ex$n_COPD_by_ctime_severity[,3],
                        copd_GOLD3=output_ex$n_COPD_by_ctime_severity[,4],
                        copd_GOLD4=output_ex$n_COPD_by_ctime_severity[,5],
                        diags_true=rowSums(output_ex$n_Diagnosed_by_ctime_severity[,2:5]), # diagnosed here is true diagnosed only
                        diags_false=rowSums(output_ex$n_Overdiagnosed_by_ctime_sex),
                        diags_total=rowSums(output_ex$n_Diagnosed_by_ctime_severity[,2:5])+rowSums(output_ex$n_Overdiagnosed_by_ctime_sex)
    )

    # health outcomes
    healthOC <- data.frame(exacs=rowSums(output_ex$n_exac_by_ctime_severity),
                           exacs_mild=output_ex$n_exac_by_ctime_severity[,1],
                           exacs_mod=output_ex$n_exac_by_ctime_severity[,2],
                           exacs_sev=output_ex$n_exac_by_ctime_severity[,3],
                           exacs_vsev=output_ex$n_exac_by_ctime_severity[,4],
                           deaths=rowSums(output_ex$n_exac_death_by_ctime_severity),
                           NRT=output_ex$n_smoking_cessation_by_ctime)

    # number of case detections
    case_detection <- data.frame(case_detection=rowSums(output_ex$n_case_detection_by_ctime),
                                 CD_true_pos=output_ex$n_case_detection_by_ctime[,3],
                                 CD_false_pos=output_ex$n_case_detection_by_ctime[,2])

    # costs
    costs <- output_ex$annual_cost_ctime

    hosps <- output_ex$n_exac_by_ctime_severity[,3:4]
    hosps_cost <- input$values$cost$exac_dcost[3:4]
    hosps_cost_yr <- rowSums(t(c(hosps_cost)*t(hosps)))

    copd <- output_ex$n_COPD_by_ctime_severity[,2:5] # column 1 is gold grade 0 i.e. no copd
    main_cost <- input$values$cost$bg_cost_by_stage[2:5]
    copd_cost_yr <- rowSums(t(c(main_cost)*t(copd)))

    caseds <- output_ex$n_case_detection_by_ctime
    caseds_cost <- c(input$values$cost$cost_case_detection,
                     input$values$cost$cost_case_detection+input$values$cost$cost_outpatient_diagnosis,
                     input$values$cost$cost_case_detection+input$values$cost$cost_outpatient_diagnosis)
    caseds_cost_yr <- rowSums(t(c(caseds_cost)*t(caseds)))

    medyrs <- output_ex$medication_time_by_ctime_class[,1:4]
    medyrs_combos <- data.frame(SABA=medyrs[,1],
                                LAMA=medyrs[,3]-medyrs[,2],
                                LAMA_LABA=medyrs[,2]-medyrs[,4],
                                ICS_LAMA_LABA=medyrs[,4])
    meds_cost <- input$values$medication$medication_costs[c(2,5,7,15)]
    meds_cost_yr <- rowSums(t(c(meds_cost)*t(medyrs_combos))) + 
      output_ex$n_smoking_cessation_by_ctime*input$values$cost$cost_smoking_cessation

    costs_subcs <- data.frame(cost_total=costs,
                              cost_case_detection=caseds_cost_yr,
                              cost_treat=meds_cost_yr,
                              cost_hosp=hosps_cost_yr,
                              cost_maint=copd_cost_yr)

    results <- cbind(base,diags,healthOC,case_detection,medyrs_combos,costs_subcs)
    
    
    
    # overall results
    overall <- data.frame(n_agents=output_ex$n_agents_CD,
                          n_diagnosed=output_ex$n_diagnosed_true_CD,
                          n_CD_eligible=output_ex$n_case_detection_eligible)
    
    
    # costs <- data.frame(case_detection=input$values$cost$cost_case_detection,
    #                     OP_diagnosis=input$values$cost$cost_outpatient_diagnosis,
    #                     SABA=unname(input$values$medication$medication_costs[2]),
    #                     LAMA=unname(input$values$medication$medication_costs[5]),
    #                     LAMA_LABA=unname(input$values$medication$medication_costs[7]),
    #                     ICS_LAMA_LABA=unname(input$values$medication$medication_costs[15]),
    #                     NRT=input$values$cost$cost_smoking_cessation,
    #                     exac_mild=input$values$cost$exac_dcost[1],
    #                     exac_mod=input$values$cost$exac_dcost[2],
    #                     exac_sev=input$values$cost$exac_dcost[3],
    #                     exac_vsev=input$values$cost$exac_dcost[4],
    #                     GOLD1=input$values$cost$bg_cost_by_stage[2],
    #                     GOLD2=input$values$cost$bg_cost_by_stage[3],
    #                     GOLD3=input$values$cost$bg_cost_by_stage[4],
    #                     GOLD4=input$values$cost$bg_cost_by_stage[5])
    
    
    
    return(list(overall=overall,results=results))

    }
  

```


```{r cost table, echo=FALSE}



```




The chunk below gives an examples of how you'd adapt the costs.

Here is how all the cost subcategories are calculated. Hopefully with these plus the cose below, you can see what's going on:

Case detection = (number administered case detection X case detection cost) + (number testing positive X outpatient diagnosis cost)

Treatment = (patient years in each medication type X annual medication type cost) + (number receiving NRT X NRT cost)

Hospitalization = (number of severe exacerbation X severe exacerbation cost) + (number of very severe exacerbation X very severe exacerbation cost)

Background cost = number in each GOLD grade X corresponding GOLD grade cost


```{r changing costs, echo=FALSE}

  # I saved all the unit costs used in the original analysis in a data frame
  unit_costs <- readRDS("unit_costs.Rda")

  # I will walk you through an example of how to calculate the costs based on the output
  # In this example I willIn  just use the standard unit costs (this obviously isn't necessary because the output costs are part of the output as well, but we can use these to check our answers)

  # run model, we will use scenario S1a as an example, I'm using sample size = 10,000
  s1a <- BIA_simul(CD_method = "CDQ17", eligibility_criteria = "All patients")

  s1a_res <- s1a$results
  
  # case detection
  CD <- cbind(s1a_res$case_detection, s1a_res$CD_true_pos+s1a_res$CD_false_pos) # first column is number administered case detection, second column in number that tested positive and hence would've been sent for OP testing
  CD_unit_cost <- c(unit_costs$case_detection, unit_costs$OP_diagnosis)
  CD_cost_yr <- rowSums(t(c(CD_unit_cost)*t(CD))) # this is annual case detection costs, the output we need
  
  
  # treatment
  treat <- cbind(s1a_res$SABA, s1a_res$LAMA, s1a_res$LAMA_LABA, s1a_res$ICS_LAMA_LABA, s1a_res$NRT)
  treat_unit_cost <- c(unit_costs$SABA, unit_costs$LAMA, unit_costs$LAMA_LABA, unit_costs$ICS_LAMA_LABA, unit_costs$NRT)
  treat_cost_yr <- rowSums(t(c(treat_unit_cost)*t(treat)))
  
  # hospitalisation
  hosps <- cbind(s1a_res$exacs_sev, s1a_res$exacs_vsev)
  hosps_unit_cost <- c(unit_costs$exac_sev, unit_costs$exac_vsev)
  hosps_cost_yr <- rowSums(t(c(hosps_unit_cost)*t(hosps)))
  
  # background medical
  copd <- cbind(s1a_res$copd_GOLD1, s1a_res$copd_GOLD2, s1a_res$copd_GOLD3, s1a_res$copd_GOLD4)
  bg_unit_cost <- c(unit_costs$GOLD1, unit_costs$GOLD2, unit_costs$GOLD3, unit_costs$GOLD4)
  bg_cost_yr <- rowSums(t(c(bg_unit_cost)*t(copd)))


  
  # so for the shiny app, when the user enters their own unit costs inputs, we can simply run the above code (or something similar, I just put this together quickly, I'm sure you can come up with something more efficient) with different input values
  
  # The only issue will be that there are some costs that don't fit into any of the categories above. We can see this by comparing the sum of the subcategories with the total costs:
  
  s1a_res$cost_total - (CD_cost_yr + treat_cost_yr + hosps_cost_yr + bg_cost_yr)
  
  # can see we're missing some. I know why this is and have a solution for working around it, but it'll be easier to explain over a zoom call. So, for now, just assume that the total cost is equal to the four subcategories I have given you




```

